### 2019-01-03 Sections/physical_architectures_for_quantum_computing.tex
CV - tiny ref updates

A universal gate set can be constructed, enabling universal quantum computation to be implemented using such an encoding. All the necessary elements may be readily implemented using present-day quantum optics technology and numerous CV quantum protocols have been demonstrated in recent years \cite{bib:RevModPhys.77.513}. Most notably, very large-scale CV cluster states have been experimentally prepared in the laboratory \cite{nickmenicucci???}.

@@

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell!Measurements}, gifting us a highly-cherished entangling operation, useful for all manner of protocols (Part.~\ref{part:protocols}).

\comment{Is the Bell projection deterministic, and, can it distinguish all four?}
\comment{In CV there is a family of Bell states, instead of four: the two-mode squeezed-vacuum with different phases}

@@

It was shown by \cite{bib:menicucciFTCVCS} that the CV cluster state model can be made fault-tolerant using efficient quantum error correcting codes, sufficient to enable arbitrary scalability.

>>>>

A universal gate set can be constructed, enabling universal quantum computation to be implemented using such an encoding. All the necessary elements may be readily implemented using present-day quantum optics technology and numerous CV quantum protocols have been demonstrated in recent years \cite{bib:RevModPhys.77.513}. Most notably, very large-scale CV cluster states have been experimentally prepared in the laboratory \cite{bib:yoshikawa2016invited}.

@@

Using a 50:50 beamsplitter to implement the reverse of Bell pair preparation, one can construct a Bell analyser for performing projections in the Bell basis\index{Bell!Measurements}, gifting us a highly-cherished entangling operation, useful for all manner of protocols (Part.~\ref{part:protocols}). The measurement is deterministic, and requires only homodyne detections.

% \comment{Is the Bell projection deterministic, and, can it distinguish all four?}
% \comment{The measurement is indeed deterministic. In CV there is a continuous family of Bell states, instead of four: the two-mode squeezed-vacuum with different phases.}

@@

It was shown by \cite{bib:PhysRevLett.100.030503} that the CV cluster state model can be made fault-tolerant using quantum error correcting codes, sufficient to enable arbitrary scalability.
